Can historical data predict population responses to climate change experiments?

### 2018-06-01 precip/manuscript/pgr_predictions.tex
Final run (?) of year effects branch

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Fri Jun 01 10:57:20 2018
\begin{table}[H]
\centering
\caption{MSE of predicted log cover changes and correlations between log cover changes predicted and observed. Predictions for the cover changes in the experimental plots were generated either from the climate or no climate models. Instances where the climate model made better predictions than the no climate model are indicated with the "***". ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:corPGR}
\begin{tabular}{rllrrrl}
  \hline
 & species & stat & no climate model & climate model & diff & improved \\ 
  \hline
1 & ARTR & cor & 0.43 & 0.12 & -0.31 &  \\ 
  2 & ARTR & MSE & 0.27 & 0.39 & 0.12 &  \\ 
  3 & HECO & cor & 0.29 & 0.30 & 0.01 & *** \\ 
  4 & HECO & MSE & 0.50 & 0.51 & 0.01 &  \\ 
  5 & POSE & cor & 0.47 & 0.58 & 0.10 & *** \\ 
  6 & POSE & MSE & 0.41 & 0.40 & -0.02 & *** \\ 
  7 & PSSP & cor & 0.38 & 0.35 & -0.03 &  \\ 
  8 & PSSP & MSE & 0.41 & 0.40 & -0.01 & *** \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Fri Jun 01 15:59:31 2018
\begin{table}[H]
\centering
\caption{MSE of predicted log cover changes and correlations between log cover changes predicted and observed. Predictions for the cover changes in the experimental plots were generated either from the climate or no climate models. Instances where the climate model made better predictions than the no climate model are indicated with the "***". ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:corPGR}
\begin{tabular}{rllrrrl}
  \hline
 & species & stat & no climate model & climate model & diff & improved \\ 
  \hline
1 & ARTR & cor & 0.43 & 0.12 & -0.31 &  \\ 
  2 & ARTR & MSE & 0.27 & 0.39 & 0.12 &  \\ 
  3 & HECO & cor & 0.29 & 0.30 & 0.02 & *** \\ 
  4 & HECO & MSE & 0.50 & 0.51 & 0.01 &  \\ 
  5 & POSE & cor & 0.47 & 0.58 & 0.10 & *** \\ 
  6 & POSE & MSE & 0.41 & 0.40 & -0.01 & *** \\ 
  7 & PSSP & cor & 0.38 & 0.35 & -0.03 &  \\ 
  8 & PSSP & MSE & 0.41 & 0.40 & -0.01 & *** \\ 
   \hline
\end{tabular}
\end{table}

### 2018-06-01 precip/manuscript/pgr_predictions_by_treatment.tex
Final run (?) of year effects branch

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Fri Jun 01 10:57:23 2018
\begin{table}[H]
\centering
\caption{MSE of predicted log cover changes and correlations between log cover changes predicted and observed. Predictions for the cover changes in the experimental plots were generated either from the year effects or the climate models. Instances where the climate model made better predictions than the year effects model are indicated with the "***". ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:corPGR}
\begin{tabular}{rlllrrrl}
  \hline
 & species & Treatment & stat & no climate model & climate model & diff & improved \\ 
  \hline
1 & ARTR & Control & cor & 0.31 & -0.00 & -0.31 &  \\ 
  2 & ARTR & Control & MSE & 0.23 & 0.31 & 0.08 &  \\ 
  3 & ARTR & Drought & cor & 0.52 & 0.19 & -0.34 &  \\ 
  4 & ARTR & Drought & MSE & 0.33 & 0.34 & 0.01 &  \\ 
  5 & ARTR & Irrigation & cor & 0.55 & -0.06 & -0.61 &  \\ 
  6 & ARTR & Irrigation & MSE & 0.29 & 0.61 & 0.32 &  \\ 
  7 & HECO & Control & cor & 0.52 & 0.30 & -0.22 &  \\ 
  8 & HECO & Control & MSE & 0.28 & 0.31 & 0.03 &  \\ 
  9 & HECO & Drought & cor & 0.08 & 0.75 & 0.67 & *** \\ 
  10 & HECO & Drought & MSE & 2.13 & 1.40 & -0.73 & *** \\ 
  11 & HECO & Irrigation & cor & 0.53 & 0.04 & -0.49 &  \\ 
  12 & HECO & Irrigation & MSE & 0.52 & 0.69 & 0.18 &  \\ 
  13 & POSE & Control & cor & 0.50 & 0.55 & 0.05 & *** \\ 
  14 & POSE & Control & MSE & 0.38 & 0.39 & 0.01 &  \\ 
  15 & POSE & Drought & cor & 0.54 & 0.77 & 0.23 & *** \\ 
  16 & POSE & Drought & MSE & 0.44 & 0.41 & -0.03 & *** \\ 
  17 & POSE & Irrigation & cor & 0.51 & 0.35 & -0.16 &  \\ 
  18 & POSE & Irrigation & MSE & 0.48 & 0.40 & -0.08 & *** \\ 
  19 & PSSP & Control & cor & 0.32 & 0.36 & 0.03 & *** \\ 
  20 & PSSP & Control & MSE & 0.35 & 0.34 & -0.01 & *** \\ 
  21 & PSSP & Drought & cor & 0.52 & 0.42 & -0.11 &  \\ 
  22 & PSSP & Drought & MSE & 0.53 & 0.53 & -0.01 & *** \\ 
  23 & PSSP & Irrigation & cor & 0.45 & 0.27 & -0.18 &  \\ 
  24 & PSSP & Irrigation & MSE & 0.39 & 0.38 & -0.01 & *** \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Fri Jun 01 15:59:34 2018
\begin{table}[H]
\centering
\caption{MSE of predicted log cover changes and correlations between log cover changes predicted and observed. Predictions for the cover changes in the experimental plots were generated either from the year effects or the climate models. Instances where the climate model made better predictions than the year effects model are indicated with the "***". ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:corPGR}
\begin{tabular}{rlllrrrl}
  \hline
 & species & Treatment & stat & no climate model & climate model & diff & improved \\ 
  \hline
1 & ARTR & Control & cor & 0.31 & 0.00 & -0.31 &  \\ 
  2 & ARTR & Control & MSE & 0.23 & 0.31 & 0.08 &  \\ 
  3 & ARTR & Drought & cor & 0.52 & 0.19 & -0.33 &  \\ 
  4 & ARTR & Drought & MSE & 0.33 & 0.34 & 0.01 &  \\ 
  5 & ARTR & Irrigation & cor & 0.54 & -0.06 & -0.60 &  \\ 
  6 & ARTR & Irrigation & MSE & 0.29 & 0.61 & 0.32 &  \\ 
  7 & HECO & Control & cor & 0.52 & 0.30 & -0.22 &  \\ 
  8 & HECO & Control & MSE & 0.28 & 0.31 & 0.03 &  \\ 
  9 & HECO & Drought & cor & 0.07 & 0.75 & 0.68 & *** \\ 
  10 & HECO & Drought & MSE & 2.14 & 1.39 & -0.74 & *** \\ 
  11 & HECO & Irrigation & cor & 0.53 & 0.05 & -0.48 &  \\ 
  12 & HECO & Irrigation & MSE & 0.52 & 0.69 & 0.18 &  \\ 
  13 & POSE & Control & cor & 0.50 & 0.55 & 0.05 & *** \\ 
  14 & POSE & Control & MSE & 0.38 & 0.39 & 0.01 &  \\ 
  15 & POSE & Drought & cor & 0.55 & 0.77 & 0.22 & *** \\ 
  16 & POSE & Drought & MSE & 0.44 & 0.44 & -0.00 & *** \\ 
  17 & POSE & Irrigation & cor & 0.52 & 0.35 & -0.17 &  \\ 
  18 & POSE & Irrigation & MSE & 0.48 & 0.40 & -0.08 & *** \\ 
  19 & PSSP & Control & cor & 0.33 & 0.36 & 0.03 & *** \\ 
  20 & PSSP & Control & MSE & 0.35 & 0.34 & -0.01 & *** \\ 
  21 & PSSP & Drought & cor & 0.53 & 0.42 & -0.11 &  \\ 
  22 & PSSP & Drought & MSE & 0.53 & 0.53 & -0.01 & *** \\ 
  23 & PSSP & Irrigation & cor & 0.45 & 0.27 & -0.18 &  \\ 
  24 & PSSP & Irrigation & MSE & 0.39 & 0.38 & -0.01 & *** \\ 
   \hline
\end{tabular}
\end{table}
